A Survey on Ordered Binary Decision Diagrams

### 2015-09-15 paper.tex
Revise Abstract
Revise Introduction

\begin{abstract}
This paper serves as a survey on \textit{ordered binary Decision diagrams}
(\textit{OBDDs}). It provides an overview of the OBDD representation, the
operations which can be applied efficiently on OBDDs and some aspects when it
comes to implementing OBDD packages. Moreover, their limitations and their
application in symbolic model checking are outlined and alternative representations
are presented to tackle these limitations. As this is just a survery, no new
insights are provided.
\end{abstract}

@@

\textit{Binary decision diagrams} (\textit{BDDs}) have been well studied since
Lee~\cite{LEE59} and especially Akers~\cite{AKERS78} introduced them. BDDs
represent a Boolean function $f$ as an acyclic, directed graph (DAG). The function
arguments may be omitted in some cases to keep the formulas simple, i.e. $f$
denotes $f(x_1, \ldots, x_2)$. Nodes represent variables and have one incoming
and two outgoing edges, each of which denotes the variable evaluates to 0 (left)
or 1 (right), respectively. Whenever the result of $f$ is fixed, an edge points
to one of the constant functions \textbf{0} or \textbf{1}. To evaluate $f$ for a
given variable assignment, one just follows the path for the respective variable
values. As soon as the path ends up in a constant, i.e. \textbf{0} or \textbf{1},
this is the result of the corresponding variable assignment. Akers~\cite{AKERS78}
already provided some techniques to simplify the BDD representation such as
combining equivalent nodes.

Figure~\ref{subfig:bdd} shows an example of a BDD representing the Boolean function
$f=(A \land B) \lor (B \land C)$. To simplify the graphs, the diagram style of
Bryant~\cite{BRYANT92} is reused, i.e. edge labels are skipped. Instead dashed
and solid lines are used to represent the value of the decision variable to be 0
and 1, respectively. This diagram style is used throughout this paper.

\begin{figure}[ht]
    \centering
    \subfigure[BDD]{
        \includestandalone[height = 3cm]{figs/bdd}
        \label{subfig:bdd}
    }
    \hskip1cm
    \subfigure[OBDD]{
        \includestandalone[height = 3cm]{figs/obdd}
        \label{subfig:obdd}
    }
    \caption{BDD and OBDD of $f=(A \land B) \lor (B \land C)$.}
    \label{fig:bdd-and-obdd}
\end{figure}

However, Bryant~\cite{BRYANT86} introduced some restrictions concerning the
ordering of the so-called \textit{decision variables} represented by the nodes
of the BDD. Furthermore, Bryant\cite{BRYANT86} was able to derive a reduced
representation of BDDs providing the DAG in a canonical form: the
\textit{Reduced Ordered Binary Decision Diagram} (\textit{ROBDD}; mostly referred
to as \textit{OBDD}, even by Bryant himself). In this paper, the terms ROBDD and
OBDD are used synonymously.

Figure~\ref{subfig:obdd} shows one possible ROBDD representation of
$f$. The following section covers the details of how
to derive the OBDD representation from a BDD. \tbr

>>>>

\begin{abstract}
This paper serves as a survey on \textit{ordered binary Decision diagrams}
(\textit{OBDDs}). It provides an overview of the OBDD representation, the
operations which can be applied efficiently on OBDDs and some aspects when it
comes to implementing OBDD packages. Moreover, their limitations and their
application in symbolic model checking are outlined and alternative representations
are presented to tackle these limitations. As this is just a survery, no new
insights are provided whatsoever.
\end{abstract}

@@

\textit{Binary decision diagrams} (\textit{BDDs}) have been well studied since
Lee~\cite{LEE59} and especially Akers~\cite{AKERS78} introduced them. BDDs
represent a Boolean function $f$ as an acyclic, directed graph (DAG). The function
arguments may be omitted in some cases to keep the formulas simple, i.e. $f$
denotes $f(x_1, \ldots, x_n)$. Nodes represent variables and have one incoming
and two outgoing edges, each of which denotes the evaluation of the variable to
0 (left) or 1 (right). Whenever the result of $f$ is fixed, an edge points
to one of the constant functions \textbf{0} or \textbf{1}. To evaluate $f$ for a
given variable assignment, one just follows the path for the respective variable
values, starting from the root. As soon as the path ends up in a constant, i.e.
\textbf{0} or \textbf{1}, this is the result of the corresponding variable
assignment. Akers~\cite{AKERS78} already provided some techniques to simplify the
BDD representation, such as combining equivalent nodes.

Figure~\ref{subfig:bdd} shows an example of a BDD representing the Boolean function
$f=(A \land B) \lor (B \land C)$. To simplify the graphs, the diagram style of
Bryant~\cite{BRYANT92} is reused, i.e. edge labels are skipped. Instead, dashed
and solid lines are used to represent the value of the decision variable to be 0
and 1, respectively. This diagram style is used throughout this paper.

\begin{figure}[ht]
    \centering
    \subfigure[BDD]{
        \includestandalone[height = 3cm]{figs/bdd}
        \label{subfig:bdd}
    }
    \hskip1cm
    \subfigure[OBDD]{
        \includestandalone[height = 3cm]{figs/obdd}
        \label{subfig:obdd}
    }
    \caption{BDD and OBDD of $f=(A \land B) \lor (\overline{B} \land C)$.}
    \label{fig:bdd-and-obdd}
\end{figure}

However, Bryant~\cite{BRYANT86} introduced some restrictions concerning the
ordering of the so-called \textit{decision variables}, represented by the nodes
of the BDD. As a consequence, Bryant\cite{BRYANT86} was able to derive a reduced
representation of BDDs providing the DAG in a canonical form: the
\textit{Reduced Ordered Binary Decision Diagram} (\textit{ROBDD}; mostly referred
to as \textit{OBDD}, even by Bryant himself). In this paper, the terms ROBDD and
OBDD are used synonymously.

Figure~\ref{subfig:obdd} shows one possible ROBDD representation of $f$. The
following section covers the details on how to derive the OBDD representation
from a given BDD.
